---
title: 'Gov 2001: Extension 2'
author: "Sima Biondi, Priyanka Sethy, Natalie Ayers"
date: "2022-11-29"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(foreign)
library(mediation)
library(gsfuns)
library("sandwich")
library("lmtest")
library("stargazer")
library("lfe")
library("plm")
library(here)
library(ggplot2)
library("jtools")
```

# Introduction

We are extending "Redemption through Rebellion: Border Change, Lost Unity, and Nationalist Conflict.” (2022), by Lars-Erik Cederman, Seraina Rüegger, and Guy Schvitz. The data and code for this paper are in the [Harvard Dataverse](https://doi.org/10.7910/DVN/SLWCLZ).

# Results

```{r ingest and prepare data}


## Load dataset
exten.df = read.csv(here("epr_segment_level_analysis_extensions_rugged_claims.csv"))

## Code "peaceyears" variable: years since last conflict, squared, cubed
exten.df$pys <- exten.df$peaceyears
exten.df$pys2 <- exten.df$peaceyears^2
exten.df$pys3 <- exten.df$peaceyears^3
exten.df$downgr5_aut = as.factor(exten.df$downgr5_aut)

## Subset dataset: only politically relevant groups (EPR definition), exclude 
## dominant and monopoly groups and groups without settlement area in GeoEPR, 
exten.df.sub.allyears <- exten.df %>%
  filter(isrelevant==1,
         status_monopoly==0,
         status_dominant==0,
         !is.na(seg_area_sqkm),
         !is.na(onset_do_flag))
```

## Table 1


### Table 1 with Mean Terrain Ruggedness and AG post-inclusion/post-downgrade

The table below replicates Table 1 in Cederman et al. (2022), providing the results of 3 logit models with robust standard errors clustered at the AG level. 

```{r generate Table 1 logit analysis, warning=FALSE, results='asis', header=FALSE}
# define variables for use in all models, including DV
vars_logit <- c("onset_do_flag", "ln_ag_area_sqkm", "ag_incidence_flag_lag",
                "status_excl", "downgraded2", "rugged_mean",
                "rbal", "warhist", "ln_capdist", "ln_rgdppc_lag",
                "ln_pop_lag",  "colonial_past", "ln_state_age",
                "pys", "pys2", "pys3",  "downgr5_aut", "downgr5_incl")
# identify AG "treatment" variables to be analyzed separately
treat.vars <- c("split", "tfrac", "tfrac_incr_post1946")

# for each "treatment" variable, run logit model
for(treat_var in treat.vars){
  full_lhs <- append(treat_var, vars_logit)
  onset_logit <- glm(onset_do_flag ~ ., 
                     data=exten.df.sub.allyears[,full_lhs], family="binomial")
  assign(paste0("logit_",treat_var), onset_logit)
}

# include clustered standard errors for each generated model
logit_split_coefs <- coeftest(logit_split, 
                              vcov. = vcovCL(logit_split, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_coefs <- coeftest(logit_tfrac, 
                              vcov. = vcovCL(logit_tfrac, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_1946_coefs <- coeftest(logit_tfrac_incr_post1946, 
                                   vcov. = vcovCL(logit_tfrac_incr_post1946, 
                                                  cluster = exten.df.sub.allyears$ag_id))

# Display results of logit model
stargazer(logit_split_coefs, logit_tfrac_coefs, logit_tfrac_1946_coefs,
          type="text",
          dep.var.labels.include = T,
          header = T,
          omit = c("pys", "pys2","pys3"),
          column.sep.width = "3pt", # to reduce column width
          single.row = TRUE, # to put coefficients and standard errors on same line
          font.size = "small", # to make font size smaller
          title = "Replication of Table 1 with Terrain Ruggedness and Lost Autonomy",
          dep.var.caption = "Civil Conflict Onset",
          covariate.labels = c("Divided group", "Fractionalization", 
                               "Frac. incr. since 1946", "Territory sq.km, log",
                               "Ongoing conflict, lag", "Exclusion", "Downgraded", 
                               "Terrain Ruggedness (Mean)","Relative size", "War history",
                               "Distance to capital, log", "GDP, lag, log",
                               "Population, log","Colonial history",
                               "State age, log",
                               "Downgrade of autonomy (5 years)", "Downgrade of inclusion (5 years)"))


```
```{r}
logit_split
```


```{r prediction plot}
effect_plot(logit_split, 
            pred = downgr5_aut, interval = T,
            x.label = "Downgrade in autonomy within last 5 years",
            y.label = "Onset of civil conflict",
            title = "test"
            )

ggsave("ext2_autonomy_prediction_plot.jpeg")

```

## For Appendix

### Cederman et al. Table 1 with Median Terrain Ruggedness and AG post-inclusion/post-downgrade

```{r generate Table 1 logit analysis, warning=FALSE, results='asis', header=FALSE}
# define variables for use in all models, including DV
vars_logit <- c("onset_do_flag", "ln_ag_area_sqkm", "ag_incidence_flag_lag",
                "status_excl", "downgraded2", "rugged_med",
                "rbal", "warhist", "ln_capdist", "ln_rgdppc_lag",
                "ln_pop_lag",  "colonial_past", "ln_state_age",
                "pys", "pys2", "pys3",  "downgr5_aut", "downgr5_incl")
# identify AG "treatment" variables to be analyzed separately
treat.vars <- c("split", "tfrac", "tfrac_incr_post1946")

# for each "treatment" variable, run logit model
for(treat_var in treat.vars){
  full_lhs <- append(treat_var, vars_logit)
  onset_logit <- glm(onset_do_flag ~ ., 
                     data=exten.df.sub.allyears[,full_lhs], family="binomial")
  assign(paste0("logit_",treat_var), onset_logit)
}

# include clustered standard errors for each generated model
logit_split_coefs <- coeftest(logit_split, 
                              vcov. = vcovCL(logit_split, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_coefs <- coeftest(logit_tfrac, 
                              vcov. = vcovCL(logit_tfrac, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_1946_coefs <- coeftest(logit_tfrac_incr_post1946, 
                                   vcov. = vcovCL(logit_tfrac_incr_post1946, 
                                                  cluster = exten.df.sub.allyears$ag_id))

# Display results of logit model
stargazer(logit_split_coefs, logit_tfrac_coefs, logit_tfrac_1946_coefs,
          type="latex",
          dep.var.labels.include = T,
          header = T,
          omit = c("pys", "pys2","pys3"),
          column.sep.width = "3pt", # to reduce column width
          single.row = TRUE, # to put coefficients and standard errors on same line
          font.size = "small", # to make font size smaller
          title = "Replication of Table 1 with Terrain Ruggedness (Median) and Lost Autonomy",
          dep.var.caption = "Civil Conflict Onset",
          covariate.labels = c("Divided group", "Fractionalization", 
                               "Frac. incr. since 1946", "Territory sq.km, log",
                               "Ongoing conflict, lag", "Exclusion", "Downgraded", 
                               "Terrain Ruggedness (Median)","Relative size", "War history",
                               "Distance to capital, log", "GDP, lag, log",
                               "Population, log","Colonial history",
                               "State age, log",
                               "Downgrade of autonomy (5 years)", "Downgrade of inclusion (5 years)"))
```


### Cederman et al. Table 1 with Median Terrain Ruggedness and AG post-inclusion/post-downgrade

```{r generate Table 1 logit analysis, warning=FALSE, results='asis', header=FALSE}
# define variables for use in all models, including DV
vars_logit <- c("onset_do_flag", "ln_ag_area_sqkm", "ag_incidence_flag_lag",
                "status_excl", "downgraded2", "rugged_range",
                "rbal", "warhist", "ln_capdist", "ln_rgdppc_lag",
                "ln_pop_lag",  "colonial_past", "ln_state_age",
                "pys", "pys2", "pys3",  "downgr5_aut", "downgr5_incl")
# identify AG "treatment" variables to be analyzed separately
treat.vars <- c("split", "tfrac", "tfrac_incr_post1946")

# for each "treatment" variable, run logit model
for(treat_var in treat.vars){
  full_lhs <- append(treat_var, vars_logit)
  onset_logit <- glm(onset_do_flag ~ ., 
                     data=exten.df.sub.allyears[,full_lhs], family="binomial")
  assign(paste0("logit_",treat_var), onset_logit)
}

# include clustered standard errors for each generated model
logit_split_coefs <- coeftest(logit_split, 
                              vcov. = vcovCL(logit_split, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_coefs <- coeftest(logit_tfrac, 
                              vcov. = vcovCL(logit_tfrac, 
                                             cluster = exten.df.sub.allyears$ag_id))
logit_tfrac_1946_coefs <- coeftest(logit_tfrac_incr_post1946, 
                                   vcov. = vcovCL(logit_tfrac_incr_post1946, 
                                                  cluster = exten.df.sub.allyears$ag_id))

# Display results of logit model
stargazer(logit_split_coefs, logit_tfrac_coefs, logit_tfrac_1946_coefs,
          type="latex",
          dep.var.labels.include = T,
          header = T,
          omit = c("pys", "pys2","pys3"),
          column.sep.width = "3pt", # to reduce column width
          single.row = TRUE, # to put coefficients and standard errors on same line
          font.size = "small", # to make font size smaller
          title = "Replication of Table 1 with Terrain Ruggedness (Range) and Lost Autonomy",
          dep.var.caption = "Civil Conflict Onset",
          covariate.labels = c("Divided group", "Fractionalization", 
                               "Frac. incr. since 1946", "Territory sq.km, log",
                               "Ongoing conflict, lag", "Exclusion", "Downgraded", 
                               "Terrain Ruggedness (Range)","Relative size", "War history",
                               "Distance to capital, log", "GDP, lag, log",
                               "Population, log","Colonial history",
                               "State age, log",
                               "Downgrade of autonomy (5 years)", "Downgrade of inclusion (5 years)"))
```

### Examine Terrain Ruggedness

```{r study terrain ruggedness}
vars_logit <- c("rugged_mean","split", "ln_ag_area_sqkm", "ag_incidence_flag_lag",
                "status_excl", "downgraded2", 
                "rbal", "warhist", "ln_capdist", "ln_rgdppc_lag",
                "ln_pop_lag",  "colonial_past", "ln_state_age",
                "pys", "pys2", "pys3",  "downgr5_aut", "downgr5_incl")

full_lhs <- append(treat_var, vars_logit)
test_ruggedness <- lm(rugged_mean ~ ., data = exten.df.sub.allyears[,full_lhs])

stargazer(test_ruggedness,
          type="latex",
          dep.var.labels.include = T,
          header = T,
          omit = c("pys", "pys2","pys3"),
          column.sep.width = "3pt", # to reduce column width
          single.row = TRUE, # to put coefficients and standard errors on same line
          font.size = "small", # to make font size smaller
          title = "Terrain Ruggedness Accounted for by Other Controls",
          dep.var.caption = "Terrain Ruggedness",
          covariate.labels = c("Divided group",  
                               "Territory sq.km, log",
                               "Ongoing conflict, lag", "Exclusion", "Downgraded", 
                               "Relative size", "War history",
                               "Distance to capital, log", "GDP, lag, log",
                               "Population, log","Colonial history",
                               "State age, log",
                               "Downgrade of autonomy (5 years)", "Downgrade of inclusion (5 years)"))
```


# References

Cederman, Lars-Erik, Seraina Rüegger, and Guy Schvitz. 2022. “Redemption through Rebellion: Border Change, Lost Unity, and Nationalist Conflict.” American Journal of Political Science 66 (1): 24–42. https://doi.org/10.1111/ajps.12634.

Carter, David B., Andrew C. Shaver, and Austin L. Wright. 2019. “Places to Hide: Terrain, Ethnicity, and Civil Conflict.” The Journal of Politics, September. https://doi.org/10.1086/704597.

Fearon, James D., and David D. Laitin. 2003. “Ethnicity, Insurgency, and Civil War.” American Political Science Review 97 (1): 75–90. https://doi.org/10.1017/S0003055403000534.

Shaver, A., Carter, D. B., & Shawa, T. W. (2019). Terrain ruggedness and land cover: Improved data for most research designs. Conflict Management and Peace Science, 36(2), 191–218. https://doi-org.ezp-prod1.hul.harvard.edu/10.1177/0738894216659843


### Sources Used

https://stackoverflow.com/questions/16498849/logistic-regression-with-robust-clustered-standard-errors-in-r

https://www.r-bloggers.com/2021/05/clustered-standard-errors-with-r/

https://statisticsglobe.com/name-variables-in-for-loop-dynamically-in-r

https://unc-libraries-data.github.io/R-Open-Labs/Extras/Stargazer/Stargazer.html


