---
title: "PS6: Replication Paper Exercise"
output: pdf_document
author: Natalie Ayers
date: "2022-10-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages and set wd, echo=FALSE, message=FALSE, results='hide'}
library(foreign)
library(mediation)
library(gsfuns)
library("sandwich")
library("lmtest")
library("stargazer")

## Set working directory to own project folder
#setwd("./redemption-through-rebellion-dataverse_files/")
```

## Publication Information

\textbf{Team Members:} Natalie Ayers, Sima Biondi, and Priyanka Sethy

\textbf{Assigned TF:} Uma Ilavarasan

\textbf{Publication:} Cederman, Lars-Erik, Seraina Rüegger, and Guy Schvitz. 2022. “Redemption through Rebellion: Border Change, Lost Unity, and Nationalist Conflict.” American Journal of Political Science 66(1): 24–42.


## Replication
### Replication of Mediation Analysis: Figure 8

\textbf{This code directly copied from Dataverse replication files.}

```{r setup for mediation model}
## Load dataset
an.df <- read.dta("epr_segment_level_analysis.dta")

## Code "peaceyears" variable: years since last conflict, squared, cubed
an.df$pys <- an.df$peaceyears
an.df$pys2 <- an.df$peaceyears^2
an.df$pys3 <- an.df$peaceyears^3

## Subset dataset: only politically relevant groups (EPR definition), exclude 
## dominant and monopoly groups and groups without settlement area in GeoEPR, 
## subset to pre-2013 years (SDM coverage only up to 2013)
an.df.sub <- an.df %>%
  filter(isrelevant==1,
         status_monopoly==0,
         status_dominant==0,
         !is.na(seg_area_sqkm),
         !is.na(onset_do_flag),
         year <= 2013)
################################################################################
## Helper Functions
################################################################################

## Function to build mediation model formulas (see package: "mediation")
makeForms <- function(dep.var, med.var, treat.var, controls){
  ## dep.var: dependent variable
  ## med.var: mediator variable
  ## treat.var: main explanatory variable
  ## controls: vector of controls
  ## returns a list with two formulas: 1: outcome model. 2: mediator model
  
  RHS <- paste(c(treat.var, med.var, controls), collapse="+")
  out <- as.formula(paste(dep.var, RHS, sep= "~"))
  
  RHS <- paste(c(treat.var, controls), collapse="+")
  med <- as.formula(paste(med.var, RHS, sep= "~"))
  
  return(list("outcome" = out,
              "mediation" = med))
}

## Function for running mediation models one by one
runMediation <- function(out.fun, med.fun, treat.var, med.var, df){
  ## out.fun:   formula with outcome variable as dv
  ## med.fun:   formula with mediator variable as dv
  ## treat.var: name of "treatment" variable
  ## med.var:   name of mediator variable
  ## df:        analysis dataframe
  o <- glm(out.fun, data = df, family = binomial(link="probit"))
  m <- glm(med.fun, data = df, family = binomial(link="probit"))
  mm <- mediate(m, o, sims = 200, treat = treat.var,
                mediator = med.var, robustSE = T)
  return(list(out.model=o,
              med.model = m,
              med.full = mm))
}

## Function to run multiple mediation models at once (alternative mediator vars)
multiMed <- function(dep.var, med.vars, treat.var, ctrls, df){
  ## dep.var:     dependent variable
  ## med.vars:    vector of alternative mediator variables
  ## treat.var:   name of "treatment" variable
  ## ctrls:       vector of control variables
  ## df:          analysis dataframe
  med.list <- lapply(1:length(med.vars), function(x){
    med.var <- med.vars[x]
    f.list <- makeForms(dep.var, med.var, treat.var, ctrls)
    med.out <- runMediation(f.list$outcome, f.list$mediation,
                            treat.var, med.var, df)
    return(med.out$med.full)
  })
  names(med.list) <- med.vars
  return(med.list)
}


################################################################################
## Model setup
################################################################################

## Define "treatment" and dependent variable
treat.v <- "tfrac_incr_post1946"
dep.v <- "onset_do_flag"

## Define control variables
ctrls <- c("ln_ag_area_sqkm", "ag_incidence_flag_lag",
           "rbal", "warhist", "ln_rgdppc_lag",
           "ln_pop_lag", "ln_capdist", "colonial_past", "ln_state_age",
           "pys", "pys2", "pys3")
```

```{r plot Figure 8}
################################################################################
## Main mediation model (Figure 8)
################################################################################
med.vars <- "allclaim2"
med.mods <- multiMed(dep.v, med.vars, treat.v, ctrls, an.df.sub)

## Plot results
plot(med.mods[[1]], treatment="treated",
     main = "Mediator:\nSecessionist / Irredentist claims", xlim=c(-0.005, 0.16))
```

### Replication of Conflict Onset Logits (Table 1)

\textbf{Recreated in R from Stata code provided in rep files}

```{r setup for regression}
vars_logit <- c("onset_do_flag", "ln_ag_area_sqkm", "ag_incidence_flag_lag",
           "status_excl", "downgraded2",
           "rbal", "warhist", "ln_capdist", "ln_rgdppc_lag",
           "ln_pop_lag",  "colonial_past", "ln_state_age",
           "pys", "pys2", "pys3")

treat.vars <- c("split", "tfrac", "tfrac_incr_post1946")
```

```{r run logit}
# apologies for the for loop
for(treat_var in treat.vars){
  full_lhs <- append(treat_var, vars_logit)
  onset_logit <- glm(onset_do_flag ~ ., 
                   data=an.df[,full_lhs], family="binomial")
  assign(paste0("logit_",treat_var), onset_logit)
}
```

The below portion of the replication needs a bit more attention, I believe, to ensure the R regression and clustered errors are performing the same as the Stata logit that was run by the authors. Nevertheless, the values are close to those in the authors' Table 1 (aside from Exclusion and Relative Size, which are very off). 

```{r obtain coef estimates}
# include clustered standard errors as in stata model
# as suggested in this stackoverflow: https://stackoverflow.com/questions/16498849/logistic-regression-with-robust-clustered-standard-errors-in-r
# and https://www.r-bloggers.com/2021/05/clustered-standard-errors-with-r/
logit_split_coefs <- coeftest(logit_split, 
                              vcov. = vcovCL(logit_split, 
                                             cluster = an.df$ag_id))
logit_tfrac_coefs <- coeftest(logit_tfrac, 
                              vcov. = vcovCL(logit_tfrac, 
                                             cluster = an.df$ag_id))
logit_tfrac_1946_coefs <- coeftest(logit_tfrac_incr_post1946, 
                                   vcov. = vcovCL(logit_tfrac_incr_post1946, 
                                                  cluster = an.df$ag_id))
```

```{r display results, warning=FALSE}
stargazer(logit_split_coefs, logit_tfrac_coefs, logit_tfrac_1946_coefs,
          type="text",
          title = "Replication of Table 1",
          dep.var.caption = "Civil Conflict Onset",
          covariate.labels = c("Divided group", "Fractionalization", 
                               "Frac. incr. since 1946", "Territory sq.km, log",
                               "Ongoing conflict, lag", "Exclusion",
                               "Downgraded", "Relative size", "War history",
                               "Distance to capital, log", "GDP, lag, log",
                               "Population, log","Colonial history",
                               "State age, log","Peace years",
                               "Peace years sq","Peace years cubed"))
```


### Resources Used

https://statisticsglobe.com/name-variables-in-for-loop-dynamically-in-r

https://unc-libraries-data.github.io/R-Open-Labs/Extras/Stargazer/Stargazer.html










